---
title: "Answers to Pertinent Questions"
author: "John Karuitha; diakingathia005@gmail.com"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
```


Please see the responses to the following questions in the **next page**.

- What are your hours of availability?
- What is your LinkedIn Profile URL?
- What is your earliest start date?
- Are you willing to work evenings (3pm-12am)?
- Do you have any professional qualifications?
- Do you have Medical Coding experience (DRG, CPT, ICD-10 coding)?
- Do you have experience writing Medical Summaries?
- What is your current country of residence?
- What university degree do you have?
- Is your degree attested by the UAE Ministry of Foreign Affairs?
- Expected minimum salary.

\newpage

\blandscape

```{r, echo = FALSE, warning = FALSE, message = FALSE}
tribble(~Issue, ~ Response, 
        
        "What are your hours of availability?", "I am available in the evenings from 1600 hours to midnight.", 
        
        "What is your LinkedIn Profile URL?", "My linkedin profile is  www.linkedin.com/in/Karuitha.", 
        
        "What is your earliest start date?", "My earliest start date would be December 1, 2022.",
        
        "Are you willing to work evenings (3pm-12am)?", "Yes.",
        
        "Do you have any professional qualifications?", "Yes, I am a Certified Accountant and Certified Information Systems Auditor.", 
        
        "Do you have Medical Coding experience (DRG, CPT, ICD-10 coding)?", "No I have no coding experience in the medical field. But I do have extensive coding experience in R, Python and SQL with advanced Ms Office and Google Suite skills.", 
        
        "Do you have experience writing Medical Summaries?", "I have not written medical summaries. However, I have experience writing research summaries in business and economics.",
        
        "What is your current country of residence?", "I reside in Kenya.", 
        
        "What university degree do you have?", "I expect to graduate with PhD in Finance in December, 2022 from the University of the Witwatersrand, Johannesburg, South Africa. I also have an MBA and a degree in Education.",
        
        "Is your degree attested by the UAE Ministry of Foreign Affairs?", "No, but the university is accreditted as a top 200 university in the world.",
        
        "Expected minimum salary.", "My salary expectation is USD 6000 per month subject to negotiations.") %>% 
        
        kbl(booktabs = TRUE, caption = "Response to Pertinent Issues") %>% 
        
        kable_classic(full_width = FALSE, 
                      latex_options = "striped") %>% 
        
        column_spec(1, width = "30em", bold = TRUE, italic = TRUE) %>% column_spec(2, width = "30em", bold = FALSE, italic = FALSE)
```

\elandscape
\newpage