% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{cochineal}
  \setmonofont[]{Fira Code}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}
    }
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{John Karuitha}
\date{07 June 2022}

% Jesus, okay, everything above this comment is default Pandoc LaTeX template. -----
% ----------------------------------------------------------------------------------
% I think I had assumed beamer and LaTex were somehow different templates.


\usepackage{kantlipsum}

\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
      {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}
    }
%\fi
\makeatother


 



%\author{\Large \vspace{0.05in} \newline\normalsize\emph{}  }


\date{}

\usepackage{titlesec}

% 
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\itshape} % \small\uppercase
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}

% add some other packages ----------

% \usepackage{multicol}
% This should regulate where figures float
% See: https://tex.stackexchange.com/questions/2275/keeping-tables-figures-close-to-where-they-are-mentioned
\usepackage[section]{placeins}



\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \PassOptionsToPackage{hyphens}{url}\usepackage[draft,unicode=true]{hyperref}
\fi
}

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={ ()},
             pdfkeywords = {},  
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

% Add an option for endnotes. -----



% This will better treat References as a section when using natbib
% https://tex.stackexchange.com/questions/49962/bibliography-title-fontsize-problem-with-bibtex-and-the-natbib-package



% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother



\linespread{1.05}

\newtheorem{hypothesis}{Hypothesis}

\usepackage{fontawesome}

\newcommand{\blankline}{\quad\pagebreak[2]}
\usepackage{graphicx}

\begin{document}



\hfill
\begin{minipage}[t]{1\textwidth}
\raggedleft%
{\bfseries John Karuitha }\\[.35ex]
\emph{\small Karatina University,\\
School of Business, Karatina, Kenya} \\[.35ex]
\faPhone \hspace{1 mm} \small{+254 736 917 717} \\ 
\faEnvelopeO \hspace{1 mm} \small{\tt \href{mailto:diakingathia2005@gmail.com}{\nolinkurl{diakingathia2005@gmail.com}}} \\ 
\faGlobe \hspace{1 mm} \small{\href{http://www.linkedin.com/in/karuitha/}{\tt www.linkedin.com/in/karuitha/}}\\ 
\hspace{1cm} \\
 07 June 2022 \\ 
\end{minipage}

% \vspace*{1em} 

\vspace*{1em}

Dear Sir or Madam:

\vspace*{1em}

 

% 07 June 2022
% 
% \vspace*{1em} 
% 

% % \setlength{\parindent}{16pt}
% \setlength{\parskip}{0pt}
% 
\textbf{RE: APPLICATION - LONDON SCHOOL OF ECONOMICS CLASS TEACHER}

I write to apply for the position of London School of Economics Class
Teacher at 2U Inc..

I submitted my PhD thesis in Financial Economics at the
\texttt{University\ of\ the\ Witwatersrand,\ Johannesburg} in South
Africa, expecting to graduate in June 2022. My research examined the
transformation of Microfinance Institutions in Africa. Hence, I have
well-developed knowledge in finance, rural finance and markets,
financial development and inclusion, and financial management. I have
over 15 years of experience in education, research, finance, and related
roles.

The research journey saw me gain advanced skills in data analytics- R
and Ms Excel, and SQL, and basics in Stata and Eviews. I am also
familiar with Big Data analytics ecosystems like Hadoop and Spark. As a
research assistant at the Wits Business School, I have worked with the
World Bank, IMF, MIX, and FRED data for five years.

Importantly, I embrace continuous learning, a critical personal quality
in the era of rapid technological changes that also affect data
analytics. Currently, I am undertaking data science courses and
independent data science projects. Additional information is available
on my \texttt{GitHub} account (\texttt{https://www.github.com/Karuitha})
and \texttt{Linkedin} profile page
(\texttt{https://www.linkedin.com/in/karuitha/}).

Although I am currently in academia, I have previously held professional
positions. At Twana Twitu Cares, an NGO, I was in charge of finance,
where I did financial reports for the management and donors (USAID and
AMREF). I was the project manager at NECLI, a livelihoods improvement
and environmental conservation community-based organisation funded by
the EU and DANIDA. I also worked as a macroeconomic statistician
specialising in sovereign debt with \texttt{Trounceflow} for three
months.

Given my background, I believe I can handle the tasks of London School
of Economics Class Teacher. Please feel free to contact me for further
information or clarification.

Best regards,

John Karuitha.

\end{document}
